Patterns in Knowledge Production: Political Ruptures and Imperial Dynamics Shaping Public Discourse in Sweden and Finland, 1640–1828

### 2017-10-11 inst/examples/20170201-manuscript.Rmd
ok

```{r Fig2, message=FALSE, warning=FALSE, fig.width=10, fig.height=4, echo=FALSE}
library(dplyr)
library(ggplot2)
theme_set(theme_bw(20))
df <- df0 %>% filter(publication_year >=1640 & publication_year <=1828) %>%
        group_by(catalog, publication_decade) %>% tally()
p <- ggplot(df, aes(x = publication_decade, y = n,
                    shape = catalog,
		    color = catalog)) + 
       geom_point(size = 4) + 
       geom_line(size = 1) + 
       ylab("Documents (n)") + xlab("Publication year") +
       #scale_color_manual(values = c("blue", "darkgreen")) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) +        
       guides(
         shape = guide_legend(title = "Catalog", reverse = TRUE),
         color = guide_legend(title = "Catalog", reverse = TRUE)	 
       ) +
       ggtitle("Title count") +
       scale_color_stata()
print(p)
```

@@

  p <- p + ggtitle(paste("Paper consumption (", catal, ")", sep = "")) +
         scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(df2$publication_decade) + 50)) + 
         scale_y_continuous(breaks = seq(0, max(df2$paper), 2e6), label = scientific_10)

@@

pics <- list()
brs <- seq(min(decade(df$publication_year)), max(decade(df$publication_year)), 10)
for (catal in unique(df$catalog)) {
  pics[[catal]] <- ggplot(subset(df, catalog == catal),
       aes(x = publication_year, y = title_length)) +
       geom_point(aes(size = n)) +
       geom_smooth(color = "black") +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +   
       ggtitle(paste("Mean title length (", catal, ")", sep = "")) + 
       xlab("Publication year") +
       ylab("Title length (words)")
}

>>>>

```{r Fig2, message=FALSE, warning=FALSE, fig.width=10, fig.height=4, echo=FALSE}
library(dplyr)
library(ggplot2)
theme_set(theme_bw(20))
df <- df0 %>% filter(publication_year >=1640 & publication_year <=1828) %>%
        group_by(catalog, publication_decade) %>% tally()

brsy <- seq(0, 1e4, 2000)
p <- ggplot(df, aes(x = publication_decade, y = n,
                    shape = catalog,
		    color = catalog)) + 
       geom_point(size = 4) + 
       geom_line(size = 1) + 
       ylab("Title count (n)") + xlab("Publication year") +
       #scale_color_manual(values = c("blue", "darkgreen")) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) +
       scale_y_continuous(breaks = brsy, labels = brsy) +
       guides(
         shape = guide_legend(title = "Catalog", reverse = TRUE),
         color = guide_legend(title = "Catalog", reverse = TRUE)	 
       ) +
       ggtitle("Title count") +
       scale_color_stata()
print(p)
```

@@

  p <- p + ggtitle(paste("Paper consumption (", catal, ")", sep = "")) +
         scale_x_continuous(breaks = brs,
	   labels = insert_minor(brs, 5, start = century(min(df2$publication_decade)))) + 
         scale_y_continuous(breaks = seq(0, max(df2$paper), 2e6), label = scientific_10)

@@

pics <- list()
brs <- seq(min(decade(df$publication_year)), max(decade(df$publication_year)), 10)
for (catal in unique(df$catalog)) {
  pics[[catal]] <- ggplot(subset(df, catalog == catal),
       aes(x = publication_year, y = title_length)) +
       geom_point(aes(size = n)) +
       geom_smooth(color = "black") +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +
       scale_y_continuous(limits = c(0, max(df$title_length))) +
       ggtitle(paste("Mean title length (", catal, ")", sep = "")) + 
       xlab("Publication year") +
       ylab("Title length (words)")
}
